Agile Inter-team Software Development

### 2019-01-20 Draft/Draft.tex
Add title. Make author information more formal.
Removing ACM reference formatting.

%
% The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
\title{Draft of Paper for SER - 574}

@@

\author{Ruben Acuna}
\affiliation{%
  \institution{Arizona State University}
  \streetaddress{Tempe}
  \city{Phoenix}
  \country{USA}}
\email{ruben.acuna@asu.edu}

\author{Sarthak Tiwari}
\affiliation{%
  \institution{Arizona State University}
  \streetaddress{Tempe}
  \city{Phoenix}
  \country{USA}}
\email{sarthak.tiwari@asu.edu}

%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
\renewcommand{\shortauthors}{Ruben and Sarthak, et al.}

@@

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{Agile, Software Engineering, Process Models, Inter-team, Management}

>>>>

%
% The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
\title{Agile Inter-team Software Development}

@@

\author{Sarthak Tiwari}
\affiliation{%
  \department{School of Computing, Informatics, and Decision Systems Engineering}
  \institution{Arizona State University}
  \city{Tempe}
  \state{Arizona}
  \country{USA}}
\email{sarthak.tiwari@asu.edu}

\author{Ruben Acu{\~n}a}
\affiliation{%
  \department{School of Computing, Informatics, and Decision Systems Engineering}
  \institution{Arizona State University}
  \city{Tempe}
  \state{Arizona}
  \country{USA}}
\email{ruben.acuna@asu.edu}

%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
\renewcommand{\shortauthors}{Tiwari and Acu{\~n}a}

\settopmatter{printacmref=false}						%RA: get rid of dumb ACM reference format BLAH BLAH

@@

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{Agile, Software Engineering, Software Development, Process Models, Inter-team, Management}
